Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-12-02 draft/draft.Rmd
draft

---
title: "Air pollution and agricultural productivity in a developing country^[I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference attendees at the 2023 KER International Conference and the University of Reading. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent I document negative externalities of air pollution in the Indian agricultural sector. Using variation in pollution induced by changes in wind across years, I show that higher levels of pollution lead to decreased agricultural productivity. The negative effects of pollution are larger in areas growing more labor-intensive crops, indicating that the pollution works partly through direct effects on labor productivity. I also show that pollution from coal plants has a larger effect on agricultural productivity than other types of pollution. A back-of-the-envelope calculation indicates that aggregate output losses from pollution are substantial; 2011 total output would have been between 2.3 and 4.5 percent higher if pollution had remained at 2001 levels, depending on the crop.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

@@

rownames(yield1reducedform) <- c("wind days (10s)", " ", 
                                  "weather", "weather (expanded)", "weather (expanded, bins)",
                                  "fixed effects:", "village", "year",
                                  "observations")
kable(
      yield1reducedform, caption = "Wind direction and agricultural productivity",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2.5cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
yield3ivmain <- yield3ivmain[,-1]
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)", "(4)")
rownames(yield3ivmain) <- c("Particulate matter", "(log PM 2.5)",
                            "Weather", "Weather (expanded)", "Weather (expanded, bins)",
                            "Fixed effects:", "Village", "Year",
                            "F (first stage)", 
                            "Observations")
kable(
      yield3ivmain, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield5heterogeneity) <- c(">p(50)", "<=p(50)", ">p(50)", "<=p(50)", "")
rownames(yield5heterogeneity)[c(1, 3)] <- c("PM 2.5", "PM times rain")
rownames(yield5heterogeneity) <- c("Particulate matter", "(log PM 2.5)", "PM times Rain", "", "Weather",
                                   "Fixed effects:", "Village", "Year", 
                                   "F (1st stage, PM)", "F (1st stage, PM times rain)", 
                                   "Observations")
kable(
      yield5heterogeneity, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4.5cm") %>%
  column_spec(c(2:6),width = "1.8cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  add_header_above(c(" " = 1, "Wind" = 2, "Yield" = 2, " " = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield7ivdiffindiff) <- c("(1)", "(2)")
rownames(yield7ivdiffindiff) <- c("Particulate matter (log PM 2.5)", "", 
                                  "PM 2.5 times Coal", "",
                                  "Weather (expanded)", "Weather (expanded, bins)",
                                  "Fixed effects:", "Year", "Village",
                                  "F (PM)", "F (PM times Coal)", "Observations")
kable(
      yield7ivdiffindiff, caption = "Agricultural productivity and pollution source",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "5.5cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(7), bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(yield2naive) <- c("(1)", "(2)", "(3)", "(4)")
rownames(yield2naive) <- c("Particulate matter (log PM 2.5)", "", 
                           "Weather", "Weather (expanded)", "weather (expanded, bins)",
                           "Fixed effects:", "Village", "Year",
                           "Observations")
kable(
      yield2naive, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  kable_classic_2()

>>>>

---
title: "Air pollution and agricultural productivity in a developing country^[I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference/seminar attendees at the 2023 KER International Conference, Seoul National, the University of Reading, and the EEA. The usual disclaimer applies.]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent I document negative externalities of air pollution in the Indian agricultural sector. Using variation in pollution induced by changes in wind across years, I show that higher levels of pollution lead to decreased agricultural productivity. The negative effects of pollution are larger in areas growing more labor-intensive crops, indicating that the pollution works partly through direct effects on labor productivity. I also show that pollution from coal plants has a larger effect on agricultural productivity than other types of pollution. A back-of-the-envelope calculation indicates that aggregate output losses from pollution are substantial; 2011 total output would have been between 2.3 and 4.5 percent higher if pollution had remained at 2001 levels, depending on the crop.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

@@

rownames(yield1reducedform) <- c("wind days (10s)", " ", 
                                  "weather", "weather (expanded)", "weather (expanded, bins)",
                                  "fixed effects:", "village", "year",
                                  "observations")
kable(
      yield1reducedform, caption = "Wind direction and agricultural productivity",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2.5cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
yield3ivmain <- yield3ivmain[,-1]
colnames(yield3ivmain) <- c("(1)", "(2)", "(3)", "(4)")
rownames(yield3ivmain) <- c("Particulate matter", "(log PM 2.5)",
                            "Weather", "Weather (expanded)", "Weather (expanded, bins)",
                            "Fixed effects:", "Village", "Year",
                            "F (first stage)", 
                            "Observations")
kable(
      yield3ivmain, caption = "Pollution and agricultural productivity, IV estimates",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  #add_header_above(c(" ", "all" = 3, "monsoon" = 1, "winter" = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield5heterogeneity) <- c(">p(50)", "<=p(50)", ">p(50)", "<=p(50)", "")
rownames(yield5heterogeneity)[c(1, 3)] <- c("PM 2.5", "PM times rain")
rownames(yield5heterogeneity) <- c("Particulate matter", "(log PM 2.5)", "PM times Rain", "", "Weather",
                                   "Fixed effects:", "Village", "Year", 
                                   "F (1st stage, PM)", "F (1st stage, PM times rain)", 
                                   "Observations")
kable(
      yield5heterogeneity, caption = "Heterogeneity in the effects of pollution on productivity",
      align = "ccccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "4.5cm") %>%
  column_spec(c(2:6),width = "1.8cm") %>%
  row_spec(c(8), hline_after = TRUE) %>%
  row_spec(c(6), bold = TRUE) %>%
  add_header_above(c(" " = 1, "Wind" = 2, "Yield" = 2, " " = 1)) %>%
  kable_classic_2()

@@

# Table
colnames(yield7ivdiffindiff) <- c("(1)", "(2)")
rownames(yield7ivdiffindiff) <- c("Particulate matter (log PM 2.5)", "", 
                                  "PM 2.5 times Coal", "",
                                  "Weather (expanded)", "Weather (expanded, bins)",
                                  "Fixed effects:", "Year", "Village",
                                  "F (PM)", "F (PM times Coal)", "Observations")
kable(
      yield7ivdiffindiff, caption = "Agricultural productivity and pollution source",
      align = "cc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "5.5cm") %>%
  column_spec(c(2:3),width = "2cm") %>%
  row_spec(c(7), bold = TRUE) %>%
  row_spec(9, hline_after = TRUE) %>%
  kable_classic_2()

@@

# Table
colnames(yield2naive) <- c("(1)", "(2)", "(3)", "(4)")
rownames(yield2naive) <- c("Particulate matter (log PM 2.5)", "", 
                           "Weather", "Weather (expanded)", "weather (expanded, bins)",
                           "Fixed effects:", "Village", "Year",
                           "Observations")
kable(
      yield2naive, caption = "Particulate matter (PM 2.5) and agricultural productivity",
      align = "cccc", booktabs = TRUE, linesep = ""
      ) %>%
  footnote(
           "Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01", 
           general_title = "",
           threeparttable = TRUE,
           footnote_as_chunk = TRUE
           ) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(c(2:5),width = "2cm") %>%
  row_spec(6, bold = TRUE) %>%
  row_spec(8, hline_after = TRUE) %>%
  kable_classic_2()

### 2023-12-02 draft/draft.tex
draft

\title{Air pollution and agricultural productivity in a developing country\footnote{I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference attendees at the 2023 KER International Conference and the University of Reading. The usual disclaimer applies. All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-12-02}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind days (10s) & -0.0078*** & -0.0065*** & -0.0051*** & -0.0053***\\
 & (0.0007) & (0.0007) & (0.0007) & (0.0007)\\
weather & No & Yes & Yes & No\\
weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter & -0.941*** & -0.769*** & -0.621*** & -0.626***\\
(log PM 2.5) & (0.078) & (0.075) & (0.080) & (0.077)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
Weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
F (first stage) & 1,236 & 1,266 & 1,205 & 1,246\\
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Wind} & \multicolumn{2}{c}{Yield} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & >p(50) & <=p(50) & >p(50) & <=p(50) & \\
\midrule
Particulate matter & -0.415*** & -0.336*** & -1.026*** & -0.568*** & -0.306***\\
(log PM 2.5) & (0.114) & (0.099) & (0.060) & (0.166) & (0.077)\\
PM times Rain &  &  &  &  & 0.119***\\
 &  &  &  &  & (0.002)\\
Weather & Yes & Yes & Yes & Yes & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes & Yes\\
\midrule
F (1st stage, PM) & 597 & 482 & 675 & 428 & 674\\
F (1st stage, PM times rain) &  &  &  &  & 6,393\\
Observations & 617,804 & 649,118 & 634,342 & 632,580 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yield7ivdiffindiff}Agricultural productivity and pollution source}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2)\\
\midrule
Particulate matter (log PM 2.5) & -0.228*** & -0.223***\\
 & (0.066) & (0.065)\\
PM 2.5 times Coal & -0.250*** & -0.220***\\
 & (0.024) & (0.025)\\
Weather (expanded) & Yes & No\\
Weather (expanded, bins) & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{}\\
Year & Yes & Yes\\
Village & Yes & Yes\\
\midrule
F (PM) & 769 & 772\\
F (PM times Coal) & 231 & 205\\
Observations & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter (log PM 2.5) & -0.042*** & -0.045*** & -0.008** & -0.041***\\
 & (0.003) & (0.003) & (0.003) & (0.003)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\title{Air pollution and agricultural productivity in a developing country\footnote{I thank Ariel Ortiz-Bobea, Marc Bellemare, and David Sungho Park for comments and suggestions that greatly improved the quality of the paper, as well as conference/seminar attendees at the 2023 KER International Conference, Seoul National, the University of Reading, and the EEA. The usual disclaimer applies.}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-12-02}

@@

\caption{\label{tab:yieldtable}Wind direction and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}>{\centering\arraybackslash}p{2.5cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
wind days (10s) & -0.0078*** & -0.0065*** & -0.0051*** & -0.0053***\\
 & (0.0007) & (0.0007) & (0.0007) & (0.0007)\\
weather & No & Yes & Yes & No\\
weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
village & Yes & Yes & Yes & Yes\\
year & Yes & Yes & Yes & Yes\\
\midrule
observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtabletwo}Pollution and agricultural productivity, IV estimates}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter & -0.941*** & -0.769*** & -0.621*** & -0.626***\\
(log PM 2.5) & (0.078) & (0.075) & (0.080) & (0.077)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
Weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
F (first stage) & 1,236 & 1,266 & 1,205 & 1,246\\
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablehet}Heterogeneity in the effects of pollution on productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}>{\centering\arraybackslash}p{1.8cm}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Wind} & \multicolumn{2}{c}{Yield} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
  & >p(50) & <=p(50) & >p(50) & <=p(50) & \\
\midrule
Particulate matter & -0.415*** & -0.336*** & -1.026*** & -0.568*** & -0.306***\\
(log PM 2.5) & (0.114) & (0.099) & (0.060) & (0.166) & (0.077)\\
PM times Rain &  &  &  &  & 0.119***\\
 &  &  &  &  & (0.002)\\
Weather & Yes & Yes & Yes & Yes & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes & Yes\\
\midrule
F (1st stage, PM) & 597 & 482 & 675 & 428 & 674\\
F (1st stage, PM times rain) &  &  &  &  & 6,393\\
Observations & 617,804 & 649,118 & 634,342 & 632,580 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. The first two columns split the sample based on the median exposure (by village). The second two columns split the sample based on initial -- the first year available -- agricultural productivity. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yield7ivdiffindiff}Agricultural productivity and pollution source}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2)\\
\midrule
Particulate matter (log PM 2.5) & -0.228*** & -0.223***\\
 & (0.066) & (0.065)\\
PM 2.5 times Coal & -0.250*** & -0.220***\\
 & (0.024) & (0.025)\\
Weather (expanded) & Yes & No\\
Weather (expanded, bins) & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{}\\
Year & Yes & Yes\\
Village & Yes & Yes\\
\midrule
F (PM) & 769 & 772\\
F (PM times Coal) & 231 & 205\\
Observations & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}

@@

\caption{\label{tab:yieldtablepm}Particulate matter (PM 2.5) and agricultural productivity}
\centering
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2cm}}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
Particulate matter (log PM 2.5) & -0.042*** & -0.045*** & -0.008** & -0.041***\\
 & (0.003) & (0.003) & (0.003) & (0.003)\\
Weather & No & Yes & Yes & No\\
Weather (expanded) & No & No & Yes & No\\
weather (expanded, bins) & No & No & No & Yes\\
\textbf{Fixed effects:} & \textbf{} & \textbf{} & \textbf{} & \textbf{}\\
Village & Yes & Yes & Yes & Yes\\
Year & Yes & Yes & Yes & Yes\\
\midrule
Observations & 1,266,922 & 1,266,922 & 1,266,922 & 1,266,922\\
\bottomrule
\end{tabular}
\begin{tablenotes}[para]
\item Note: Standard errors are in parentheses and are clustered at the village level. The outcome in all regressions is estimated (log) agricultural yield, defined as tons per hectare. * p<0.10 ** p<0.05 *** p<0.01
\end{tablenotes}
\end{threeparttable}
\end{table}
